\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-25 papers/jfp/8-engineering.tex
Fix sprshN numbering

sprsh4 :: Tasks MonadFail String Integer
sprsh4 "B1" = Just $ Task $ \fetch -> do
    a1 <- fetch "A1"
    a2 <- fetch "A2"
    if a2 == 0 then fail "division by 0" else return (a1 `div` a2)
sprsh4 _ = Nothing
\end{minted}
\vspace{1mm}

@@

\begin{minted}[xleftmargin=10pt]{haskell}
sprsh3 :: Tasks MonadRandom String Integer
sprsh3 "B1" = Just $ Task $ \fetch -> do a1 <- fetch "A1"
                                         r  <- getRandom (1,2)
                                         return (a1 + r)
sprsh3 _    = Nothing
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
sprsh4 "B1" = Just $ Task $ \fetch -> do
    formula <- fetch "B1-formula"
    evalFormula fetch formula
\end{minted}
\vspace{1mm}

@@

\noindent
The function \hs{selfTracking} defined below is a generalisation of the approach
explained in the above \Excel example \hs{sprsh4}. The function takes a parser
for scripts, of type \hs{s}~\hs{->}~\hs{Task}~\hs{Monad}~\hs{k}~\hs{v}, and a
description of \emph{how to build all scripts}, of type
\hs{Tasks}~\hs{Monad}~\hs{k}~\hs{s}. For \hs{sprsh4}, the latter would simply
fetch \cmd{B1-formula} when given the key \cmd{B1} and return \hs{Nothing}
otherwise, but the presented approach can cope with much more sophisticated
scenarios where scripts themselves are derived from ``script sources'', e.g. all
C compilation scripts can be obtained from a single pattern rule, such as
\cmd{gcc -c [source] -o [object]}. The resulting typed task description
\hs{TasksT}~\hs{Monad}~\hs{(Key}~\hs{k}~\hs{v}~\hs{s)} tracks both values and
scripts that compute them, and is therefore self-tracking.

>>>>

sprsh3 :: Tasks MonadFail String Integer
sprsh3 "B1" = Just $ Task $ \fetch -> do
    a1 <- fetch "A1"
    a2 <- fetch "A2"
    if a2 == 0 then fail "division by 0" else return (a1 `div` a2)
sprsh3 _ = Nothing
\end{minted}
\vspace{1mm}

@@

\begin{minted}[xleftmargin=10pt]{haskell}
sprsh4 :: Tasks MonadRandom String Integer
sprsh4 "B1" = Just $ Task $ \fetch -> do a1 <- fetch "A1"
                                         r  <- getRandom (1,2)
                                         return (a1 + r)
sprsh4 _    = Nothing
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
sprsh5 "B1" = Just $ Task $ \fetch -> do
    formula <- fetch "B1-formula"
    evalFormula fetch formula
\end{minted}
\vspace{1mm}

@@

\noindent
The function \hs{selfTracking} defined below is a generalisation of the approach
explained in the above \Excel example \hs{sprsh5}. The function takes a parser
for scripts, of type \hs{s}~\hs{->}~\hs{Task}~\hs{Monad}~\hs{k}~\hs{v}, and a
description of \emph{how to build all scripts}, of type
\hs{Tasks}~\hs{Monad}~\hs{k}~\hs{s}. For \hs{sprsh5}, the latter would simply
fetch \cmd{B1-formula} when given the key \cmd{B1} and return \hs{Nothing}
otherwise, but the presented approach can cope with much more sophisticated
scenarios where scripts themselves are derived from ``script sources'', e.g. all
C compilation scripts can be obtained from a single pattern rule, such as
\cmd{gcc -c [source] -o [object]}. The resulting typed task description
\hs{TasksT}~\hs{Monad}~\hs{(Key}~\hs{k}~\hs{v}~\hs{s)} tracks both values and
scripts that compute them, and is therefore self-tracking.
